Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-06-04 02_paper/02_study/paper_methods.Rmd
method

@@

\@ref(fig:sri)

#### Situational Jugdement Test
To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).

Gold and Holodynski (2015, p. 229) developed a 'Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers. This is a test procedure for situation-specific action in which the participants are presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.

@@

The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers the pupils, orientation and structure in everyday school life (cf. ibid.).

When taking the test, participants must rate all six response options for each scenario as suitable or unsuitable using a six-point scale (see sample scenario in Appendix 1). Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement. Based on these, an overall rating was created, which is used for the evaluation of the answer keys. All three mentioned knowledge facets of class management (monitoring, transition design and rules and routines) are recorded separately with separate tasks in this SJT by Gold and Holodynski. The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines. Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement. In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.

@@

In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and ... 2022.

@@

After the letter search, all technical devices were turn

the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.

In the second part of the study, the experimenter conducted a Stimulated-Recall Interview (SRI) with the subject. In this interview, the recorded video of the lesson was watched and commented on by the subject while thinking aloud.

Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.

This study is subject to a quasi-experimental study design, as there was no random assignment of the test persons to the experimental conditions. Due to the use of MET technology, the study has a high external validity (Gegenfurtner et al., 2018). The SRI carried out afterwards explicitly investigates the subjects' sense of disturbance and feeling of safety, which speaks for a high content validity of the study. Internal validity can be ensured to the extent that the teaching events that occurred were exactly the same for all subjects, as the learners received precise behavioural instructions. These disturbances followed a script and coding guide in which the actions of the class were precisely described. The sequence of events varied from survey to survey so that disruptions were always random. The scripted behavioural instructions during the teaching sequence characterise this study with a high degree of standardization, especially when compared to events taking place in a real classroom. The study is based on an experimental manual, script and coding guide, which explicitly describes the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable. As this study takes place within the framework of the dissertation ProVisioNET, the original survey will continue beyond the submission of this scientific work.
continues.

>>>>

This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions. Due to the use of mobile eye-tracking technology, the study had a high external validity [@gegenfurtner2018mobiles]. Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions. These disruptions followed a script and coding scheme in which the actions of the class were precisely described. The order of the disruptions as well as the performing actors were fully balanced with Lain Square to exclude row effects.

The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom. The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.

@@

Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions. Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.

The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.

For the present study, the following two questions from the interview were relevant:
1. "How disturbing did you perceive this event to be?"
2. "How confident did you feel in dealing with this event?"

Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for "not at all disruptive" or "not at all safe" and 10 for "extremely disturbing" or "extremely safe."

With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption. Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways [@albers2009methodik, p. 67f]. In the present questionnaire, the numerical representation with eleven answer options (0-10) was used. There was no specific designated neutral position. In this questionnaire, the middle category 5 was not interpreted as a neutral position. In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time. With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales. The question remained the same for all subjects and no additional comments were made. Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified. However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.

#### Situational Jugdement Test

To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]). In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).

@@

The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers pupils orientation and structure in everyday school life (cf. ibid.).

The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany. For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management. With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf. ibid.). For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf. ibid., p. 238). Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf. ibid.).

The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf. ibid., p. 238ff). Despite limitations in reliability, the test was confirmed to have content and construct validity (cf. ibid., p. 243). On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.

The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet *monitoring*, scenarios 6-9 the facet *managing momentum* and scenarios 11-14 the facet *rules and routines*.

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study *ProVisioNET*. The objectivity of analysis was given by processing the obtained questionnaire data in `r cite_r("r-references.bib")` and IBM SPSS 28.

Since the test was a questionnaire designed to assess strategic knowledge of classroom management of *primary school teachers*, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade. Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.

@@

In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.

@@

After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices. Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature. The completion of the questionnaire took approximately 5 minutes.

In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \@ref(fig:sri). The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen. The recorded eye-tracking video was watched and commented on by the subject while thinking aloud. The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions. The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions. The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred. After the disruption occurred, the subject was asked to describe what had just happened. If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10 (for a detailed description of the scale question, see Rating Scales). In addition, the subject was asked to reason the given number. In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction. The

Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management. The
completion of the entire survey took 15 min on average.

### 2022-06-04 02_paper/02_study/paper_methods.tex
method

\begin{verbatim}
## Warning: NAs durch Umwandlung erzeugt
\end{verbatim}

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
\midrule
Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00\\
Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & NA & NA & NA & NA & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
\bottomrule
\end{tabular}

@@

The sample consists of \emph{N} = 28 participants with \emph{n} = 7 expert teachers and \emph{n} = 21 novice teachers.

@@

The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37). 71\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their NA semester (\emph{SD} = NA; range: NA-NA). Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies. 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

\hypertarget{material}{%
\subsection{Material}\label{material}}

Experimental stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .

@@

During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}). The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

\hypertarget{behavioral-data}{%
\subsubsection{Behavioral data}\label{behavioral-data}}

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (\url{https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/}) installed in the middle of the lab setting. The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (\url{https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf}) from different angles. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 2.94 & 0.26 & 2.50 & 3.38 & 0.02 & 1.69 & 0.31\\
Balance & 3.00 & 3.14 & 0.56 & 1.67 & 4.00 & -0.45 & 3.53 & 0.71\\
Presence & 8.00 & 3.10 & 0.36 & 2.50 & 3.88 & 0.10 & 2.65 & 0.66\\
Natural Behavior & 3.00 & 3.17 & 0.65 & 1.67 & 4.00 & -0.65 & 2.91 & 0.80\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 3.00 & 0.20 & 2.75 & 3.25 & 0.25 & 1.42 & -0.16\\
Balance & 3.00 & 3.43 & 0.42 & 2.67 & 4.00 & -0.57 & 2.87 & 0.41\\
Presence & 8.00 & 3.36 & 0.45 & 2.50 & 3.88 & -0.85 & 2.95 & 0.84\\
Natural Behavior & 3.00 & 3.38 & 0.36 & 3.00 & 4.00 & 0.60 & 2.36 & 0.00\\
\bottomrule
\end{tabular}

@@

\hypertarget{verbal-data}{%
\subsubsection{Verbal data}\label{verbal-data}}

In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.

@@

@@

Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}

>>>>

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
\midrule
Expert & 15 & 60.00 & 42.90 & 11.30 & 27.00 & 59.00\\
Novice & 24 & 66.70 & 23.50 & 1.80 & 20.00 & 27.00\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 15 & 15.70 & 13.30 & 2.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 60.00\\
Novice & 24 & 0.00 & 0.00 & 0.00 & 0.00 & 7.20 & 2.60 & 3.00 & 11.00 & 11.30 & 8.20 & 4.00 & 36.00 & 87.50 & NA\\
\bottomrule
\end{tabular}

@@

The sample consists of \emph{N} = 39 participants with \emph{n} = 15 expert teachers and \emph{n} = 24 novice teachers.

@@

The expert teachers (9 women; 60\%) had a mean age of 42.90 years (\emph{SD} = 11.30; range: 27-59) and an average teaching experience of 15.70 years (\emph{SD} = 13.30; range: 2-37). 60\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.

\hypertarget{xxx-type-of-school-noch-eintragen}{%
\subsubsection{XXX Type of School noch eintragen}\label{xxx-type-of-school-noch-eintragen}}

The novice teachers (16 women; 66.70\%) had a mean age of 23.50 years (\emph{SD} = 1.80; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11). Furthermore, they had an average teaching experience of 11.30 teaching units à 45min (\emph{SD} = 8.20; range: 4-36) through the internships during their studies. 87.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

@@

\hypertarget{variables}{%
\subsection{Variables}\label{variables}}

All stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .

@@

To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit. The system consisted of a wearable head unit and a recording unit. As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher's field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

\hypertarget{video-data}{%
\subsubsection{Video data}\label{video-data}}

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}. The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}. The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 2.92 & 0.25 & 2.50 & 3.38 & 0.20 & 1.76 & 0.32\\
Balance & 3.00 & 3.15 & 0.55 & 1.67 & 4.00 & -0.47 & 3.53 & 0.60\\
Presence & 8.00 & 3.12 & 0.34 & 2.50 & 3.88 & -0.08 & 2.81 & 0.64\\
Natural Behavior & 3.00 & 3.14 & 0.61 & 1.67 & 4.00 & -0.51 & 2.99 & 0.79\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
\midrule
Classroom Management & 8.00 & 3.17 & 0.27 & 2.75 & 3.62 & 0.30 & 2.21 & 0.38\\
Balance & 3.00 & 3.27 & 0.58 & 2.00 & 4.00 & -0.78 & 2.81 & 0.77\\
Presence & 8.00 & 3.44 & 0.37 & 2.50 & 3.88 & -1.10 & 3.97 & 0.74\\
Natural Behavior & 3.00 & 3.42 & 0.50 & 2.67 & 4.00 & -0.07 & 1.66 & 0.68\\
\bottomrule
\end{tabular}

@@

\hypertarget{rating-scales}{%
\paragraph{Rating scales}\label{rating-scales}}

@@

\hypertarget{situational-jugdement-test}{%
\paragraph{Situational Jugdement Test}\label{situational-jugdement-test}}

To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).

Gold and Holodynski (2015, p.~229) developed a `Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers. This is a test procedure for situation-specific action in which the participants were presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.

In developing the test procedure, the authors divided the concept of classroom management into three main aspects: \emph{Monitoring}, \emph{managing momentum} (structuring) and \emph{rules and routines} (Gold \& Holodynski, 2015, p. 230f).

\emph{Monitoring} includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.~ibid.; {[}Kounin (2006), p.~89ff).

By \emph{managing momentum} (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention (Kounin, 2006, p. 101ff). They also include the group focus specifically identified by Kounin (Kounin, 2006, p. 117ff), i.e.~mobilizing the whole class and demanding accountability (Gold \& Holodynski, 2015, p. 231).

The third facet of classroom management, establishing \emph{rules, routines and rituals}, supports the other two facets and offers pupils orientation and structure in everyday school life (cf.~ibid.).

In the questionnaire, subjects were asked to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario).

Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement. Based on these, an overall rating was created, which is used for the evaluation of the answer keys. All three mentioned knowledge facets of class management (monitoring, managing momentum and rules and routines) were recorded separately with separate tasks in this SJT by Gold and Holodynski. The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines. Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement. In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.

The SJT is a standardized test in which the instructions are explicitly specified. When creating the test, the 14 constructed scenarios with 5-7 response options were first subjected to an expert survey to examine the content validity (Gold \& Holodynski, 2015, p. 235f). With the exception of scenario 5, which was subsequently excluded, the 17 experts certified an appropriate level of content validity for all other scenarios (cf.~ibid.). For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.~ibid., p.~238). Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.~ibid.). The construct validity of the SJT with the remaining 11 scenarios and the sensitivity to differences in subject knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.~ibid., p.~238ff). Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.~ibid., p.~243). On the basis of these results, a sufficient reliability and validity of the SJT test procedure is assumed. Objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in the statistical program SPSS.

@@

Finally, the subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management. The
completion of the entire survey took 15 min on average.

@@

All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}

\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
